Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-05-21 doc/mc-paper.tex
Minor edits

We summarize the results of our experiments here.  
The supplement~\cite{bryant:sat:2023:supplement}
provides a more complete description. For our
evaluation, we used the public benchmark problems from the 2022
standard and weighted model competitions\footnote{Downloaded from \url{https://mccompetition.org/2022/mc_description.html}}.  We found that there were
180 unique CNF files among these, ranging in size from 250 to
2,753,207 clauses.
%%We ran our programs on a processor with 64~GB of
%%memory and having an attached high-speed, solid-state
%%disk.
With a runtime limit of 4000 seconds, \dfour{} completed for 124 of the
benchmark problems.  Our proof generator was able to convert all of
these into POGs, with their declarations ranging from 304 to
2,761,457,765 median 848,784) defining clauses.
%(The
%maximum count overflowed the overflowed the 32-bit signed integers we
%used to represent clause identifiers in both the proof generator and
%checker.)
We ran our proof generator with a time limit of 10,000 seconds.
The results are shown in Figure~\ref{fig:dual:total}, with the plot of runtimes on the left and the plot of the total number of clauses on the right.
The proof generator was able to generate full proofs for 108 of the problems and
one-sided proofs for an additional 9 of them, leaving just 7 with no
verification.  The prototype checker successfully verified all of the generated
proofs.  The longest runtime for the combination of proof generator
and checker for a full proof was 13,145 seconds.
Overall the ratio
between the combined generation plus checking time versus the time
for \dfour{} had a harmonic mean of 5.5.
The ratio between the total number of clauses and the number of defining clauses had a harmonic mean of 3.13.
It is worth noting that, to date, we have not found
any errors in the dec-DNNF graphs generated by \dfour{}.

@@

Running the verified proof checker in \lean{} required, on average
(harmonic mean), around 5.9 times longer than the prototype checker.
Encouraging, the scaling trends were identical for the two solvers,
indicating that the two checkers have similar asymptotic performance.
We consider a factor of 5.9 to be acceptable for the assurance
provided by formal verification.

>>>>

We summarize the results of our experiments here.  
The supplement~\cite{bryant:sat:2023:supplement}
provides a more complete description. For our
evaluation, we used the public benchmark problems from the 2022
standard and weighted model competitions\footnote{Downloaded from \url{https://mccompetition.org/2022/mc_description.html}}.  We found that there were
180 unique CNF files among these, ranging in size from 250 to
2,753,207 clauses.
%%We ran our programs on a processor with 64~GB of
%%memory and having an attached high-speed, solid-state
%%disk.
With a runtime limit of 4000 seconds, \dfour{} completed for 124 of the
benchmark problems.  Our proof generator was able to convert all of
these into POGs, with their declarations ranging from 304 to
2,761,457,765 median 848,784) defining clauses.
%(The
%maximum count overflowed the overflowed the 32-bit signed integers we
%used to represent clause identifiers in both the proof generator and
%checker.)

We ran our proof generator with a time limit of 10,000 seconds.  The
results are shown in Figure~\ref{fig:dual:total}, The left-hand plot
shows the elapsed time for the combination of proof generation,
checking, and counting versus the time for
\dfour{}.  The right-hand side shows the total number of clauses in the CPOG file versus the number of defining clauses.
The proof generator was able to generate full proofs for 108 of the problems and
one-sided proofs for an additional 9 of them, leaving just 7 with no
verification.  The prototype checker successfully verified all of the generated
proofs.  The longest runtime for the combination of proof generator
and checker for a full proof was 13,145 seconds.
Overall the ratio
between the combined generation plus checking time versus the time
for \dfour{} had a harmonic mean of 5.5.
The ratio between the total number of clauses and the number of defining clauses had a harmonic mean of 3.13.
To date, we have not found
any errors in the dec-DNNF graphs generated by \dfour{}.

@@

Running the verified proof checker in \lean{} required, on average
(harmonic mean), around 5.9 times longer than the prototype checker.
Encouragingly, the scaling trends were identical for the two solvers,
indicating that the two checkers have similar asymptotic performance.
We consider a factor of 5.9 to be acceptable for the assurance
provided by formal verification.
